%4/17/2009 10:22AM
%The practice of writting a personal notes on career path.
%The strategy is very simple, just keep use \beginSections.
%\def\footline{\hss\tenrm--\folio--\hss}
\footline={\hss\tenrm--\folio--\hss}

\topglue 1in % This makes an inch of blank space (1in=2.54cm).
\centerline{\bf Resume}
\smallskip % This puts a little extra space after the title line.
\centerline{\it Eddie Wu}

% Now we use \beginsection to introduce part 1 of the document.
\beginsection {1. Profile. }% The next line must be blank!

\settabs
\+\indent&Working Experience\quad&5+ years in J2EE Development (10 years total)\cr
\+&Chinese Name         & Wu Jianfeng\cr
\+&Gender               & Male \cr
\+&Degree               & Bachelor\cr
\+&Working Experience   & 5+ years in J2EE Application Development (10 years total)\cr
\+&Mobile Phone         & 13661788694\cr
\+&Email                & ueddieu@yahoo.com.cn\cr

\section{2. Skills Summary. }

I have more than five years working experience in J2EE application development. 
Besides the outstanding  knowledge of J2EE platform and Oracle database,
I also master a lot of computer science related topic, such as Operating System Kernel,
Algorithm, regular expression, etc. 

%{bf Java} I am not only good at Java programming, but also familiar with C and C++. 
%I not only have ever read the source code of Struts, Spring and Hibernate etc.,
%but also have ever read the source code of Linux kernel. The kind of background 
%provide me a more practical and pragmatic attitude about technical.


\section{2.1. J2EE Experience. }
I have more than five years' experience of developing enterprise application in J2EE platform. 
I have ever applied the following J2EE technology in my daily work since 2004: 
SP, Servlet, JSTL, JDBC, JTA. I have 3--5 years experience in using the 
following frameworks and tools: Struts, Tapestry, Hibernate, Spring, Cactus, 
Log4J, Axis. 

For Application Server, I usually use Tomcat in development environment and
use clustered Oracle 10g Application Server in system testing environment. 
I am also familiar with WebSphere Application Server; 
I become an IBM certified Solution Developer -- WebSphere Studio, V5.0 since October of 2004.

\beginsection{2.2. Oracle Database. }\par
I believed in solid foundation and I think solid knowledge of database is
 important in building a high-performance J2EE WEB application. 
When I first time encounter performance issue in my project and successfully resolve it,
 I start to learn Oracle Database systematically; 
I became Oracle Certified Professional DBA on July of 2006. 

since that, I become the authority of Oracle database in my team and company, 
I have resolved many application
performance issue, most of them are caused by bad SQL statement. I conducted the training
to share my knownledge on Oracle. Help them to understand how a SQL statement is executed and
how to measure the performance of a SQL statement.

%Trouble shooting the perfomance issue also help me uderstand the big picture of an applicaiton.
%all the database I tuneed the performance of an application, 
which accesses Oracle database through Hibernate framework and performs bad in high load. I realized the importance of Oracle database knowledge in the J2EE platform and  

\beginsection{2.3. Design Skills. }

I have good understanding of classic GOF Design Patterns and J2EE patterns. 
It helps a lot in understanding the architecture of my projects and other 
frameworks used in projects. But I treat design pattern as a way to help you resvole the problem beautifully

I got better understanding of Object Oriented Analysis and Design after I mastered design patterns. Source code reading improve my understanding of design pattern, e.g. Visitor pattern and Interpretor pattern are widly used in javac implementation.
3
    
\beginsection{2.4 Source Code Reading.}\par
I believe Source Code Reading is an important skill for software engineer.
I have ever read the source code of Struts, Hibernate, and Spring etc., 
the knowledge of how those frameworks interally helps a lot when I trouble-shoot 
the issues happened in produciton environment.


\beginsection{2.4. English Skill}\par
I can apply English in daily work fluently as a second language. 
I not only can read and write technical document fluently in English, 
but also can communicate with native speaker in conference call.

I have ever been to San Francisco to develop a project on-site and for one month on 2007. 
Now we communicate with customer majorly through weekly conference call and email.

\beginsection{2.5 Certificates. }

I do not believe the Certificate is a good measure of my skill, but I do think
persuing a certificate can help you learn the knowledge systematically and quickly.\par
\indent
\settabs
\+\indent&2008/09\quad&PMP (Project Management Professional)\quad&92,98,87,91\quasd&\cr
\+&Date        & Certificate Name                  	& Score       & Serial Number\cr
\+&2008/09     & PMP (Project Management Professional)\cr
\+&2006/07     & Oracle DBA                              & 92,98,87,91 & \cr
\+&2004/10     & IBM Certified Solution Developer  	& 72          & \cr
\+&            & ---WebSphere Studio, V5.0         	&             & \cr
\+&2004/09     & SCJP (Sun Certified Java Programmer)    & 98          & 409182\cr
\+&2003/01     & Certified Advanced Programmer     	& $53+61$     & 02-81-13-021\cr
\+&2002/03     & Certified Programmer             	& $70+59$     & 0121400294\cr

%\midinsert % This begins inserted material, e.g., a figure.
%\narrower\narrower % This brings the margins in (see Chapter 14).
%\noindent \llap{``}If there hadn't been room for this material on
%the present page, it would have been inserted on the next one.''
%\endinsert % This ends the insertion and the effect of \narrower.

%\proclaim Theorem T. The typesetting of $math$ is discussed in
%Chapters 16--19, and math symbols are summarized in Appendix~F.


\beginsection 3. Work Experience\par

\noindent
I started my first full-time IT job from March 15, 2004, till now I have more
than five years experience on J2EE platform. Before that, I have worked in 
Phamaceutical industry for almost 5 years.
% before I started to working on IT (Informaiton Industry).

\beginsection 3.1. Shanghai Bleum Inc. (October 6, 2004--Now)\par

\noindent
I have worked in BLEUM for more than 4 year. I joined Bleum as a junior 
developer, and gradually grow up to senior developer, technical leader,
Architecture, Project manager.

\smallskip\noindent
\beginsection 3.1.1. Project Manager (May 8, 2008--Now)\par
\noindent
I start to manage the pro

\smallskip\noindent
\beginsection 3.1.2. Architect (October 8, 2007--May 8, 2008)\par
\noindent
%\beginsection{Mobile Pay Project}
%This project is to add the mobile phone as the payment channel. After the credit card holder activates this new service, he can not only receive SMS notification before payment is due, but also can query the balance and make payment through mobile phone.

%I am the project manager of this project. My major responsibility is to 
%plan and control the schedule, and to communicate with customer.

%\subsubsection{Auto-payment Project}
%The major feature of this project is making online payment for credit card account.
%We have successfully resolved the following challenges: concurrently access, resubmit, application level fail over between databases.

%As developer, my major responsibility in this project is designing, coding and Unit/Integration testing of related module according to Requirement Specification. I also directly communicate with customer to confirm requirement.


%\subsubsection{Data Synchronizing Project}
%This project includes basically three back end procedures, which are scheduled to synchronize data between different databases everyday. These back end procedures can also be started manually if necessary. We are required to re-implement  the existing implementation based on Toplink. For the convenience of performance tuning, we decide to access database through JDBC.

I am the technical leader of this project. My major responsibility is
designing, performance tuning, and Integration testing of related modules.

\smallskip\noindent
\beginsection 3.1.3. Technical Leader(May 8, 2006--May 8, 2007)\par
\noindent
This project is to add new feature --- PDF printing for a WEB site, and to change the looking and feel by using more pop up window. The PDF printing is a big challenge for us until we found a tool called PD4ML, which supports convesion from dynamic JSP content to PDF. We also verified that it can works well in the load of about twenty concurrent users. 

I am the technical leader of this project. My major achievement is the PDF printing solution based on PD4ML, which can successful convert the JSP page to PDF document. 

\smallskip\noindent
\beginsection 3.1.4. Senior Software Engineer (October 8, 2005--May 8, 2006)\par
\noindent
This project is to optimize performance of an existing application, since customer is not satisfied with the performance of the existing system. We got following lessons and experience about application performance tuning. First, we should consider performance requirement and perform load test in construction phase; Second, the load test should be based on highly-simulated environment, including same amount of data  in database. Third, Hibernate may generate some unnecessary table joins, the solution is to use native SQL instead of HQL in such case. Last but not the least, all the SQL Statement, including the SQL statement generated by Hibernate, should be reviewed to decide whether existing index is enough or not and what new index we need to add. 

I am the technical leader of this project. I not only improved the performance of the application (several SQL query speeds up more than ten times after tuning), but also gain a lot of hand on experience on Oracle database.

\smallskip\noindent
\beginsection 3.1.5. Software Engineer (December 6, 2004--October 8, 2005)\par
\noindent
The architecture this project is a little special, the business layer is located in Tibco Bizwork server, and Application server  basically is a client of the web service published by Tibco Bizwork. The major challenge in this project is to resolve the issues in using Axis, for example, memory leak issue. We also developed a mock mechanism to develop and test WEB layer when the business layer is not ready. (Business layer is joint-developed simultaneously by another two teams, one is in America and the other is in Singapore.)

I am the major developer of this project. I researched on Axis and give training about Axis to team members in the design phase. 

\beginsection 3.2. Shanghai Zhongxin Development Inc. (March 15, 2004--October 6, 2004)\par

\noindent
The application is deployed on Oracle 9i Application Server in the local area net. It is used to manage all kind of  registry and approve of Shanghai Production Security Administration Bureau. The Project achieved success in the use of Struts Framework, which saves us a lot of work. I am in charge of implementing the Business Flow module and System Manage module. 

My responsibility includes Designing, Coding, Unit/Integration testing of related module. 

\beginsection 3.3. Shanghai Zhongxi Pharmeceutical Inc. (May 28, 2001--March 12, 2004)\par

\noindent
In this period, I worked in Marketing Department providing academic support for new drugs. In my non-working time, I continually learning Java programming language and other Computer Science subject, and got the certificate of Programmer and Advanced Programmer. Then I started to be involved in the following IT projects in my leisure time.

\beginsection {3.3.1. Chinese Chess Game On Internet (2003/09 -- 2003/11). }

In this project, we need to develop an Chinese Chess Game application of Server/Client architecture. Its main features include negotiating the regulation, playing between a pairs of player through internet, watching other player's game, counting of time, and requesting to regret the step taken. The player's information is stored in the databases, and every game can been scored automatically by application. 

I am in charge of the design and implementation of the client side, implementation of chess rule in the Server side. It took me a lot of time to develop the GUI in client side and to integrate it with the server side. 

\beginsection {3.3.2. Go Game (Weiqi) Applet (2002/05 -- 2002/08). }

As an ancient Chinese game, Go is very complex. This program can help the
GO players to improve their skills especially skills in ``making live'' in the board. With
the correct strategy stored in the data file, the applet, which is downloaded from internet, can fight against the player, and beat him unless the player has master the skills. This applet improved the interactivity in the teaching and learning of Go related skill. 

I am in charge of design and implementation of the program by myself. I also build a simple  temporary WEB site to test the Applet. 


\beginsection {3.4. Suzhou NO.2 Pharmeceutical Factory (1999/07 -- 2001/05)}\par

\noindent
During this period, I worked in R\&D department and took part in the 
developing of a new chemical drug -- Paroxtine. My major responsibility 
includes chemical synthesis and chemical analysis. At the same time, 
I start to self-study Java programming language and other Computer Science subject. 

\beginsection {4. Education and Training}\par
\settabs\+\indent&July 2008\quad&\cr
\+&July 2008	&PMP Training provided by Beijing Mordern Project \cr
\+&						&Management Interchange Center\cr
\+&1994-1999	&Shengyang Pharmaceutical University\cr
\+&						&Pharmacy English (5 years)\cr



\bye % This is the way the file ends, not with a \bang but a \bye.
