%7/17/2009
%The practice of writting a personal notes on career path.
%The strategy is very simple, just keep use \beginSections.

\topglue .4in % This makes an inch of blank space (1in=2.54cm).
\centerline{\bf Resume}
\smallskip % This puts a little extra space after the title line.
\centerline{\it Eddie Wu}

%Requirements:

% BS, MS, or PhD in Computer Science or related technical discipline (or equivalent).
%
% A solid foundation in computer science, with strong competencies in data 
% structures, algorithms, and software design.
%
% Extensive programming experience in C/C++ and/or Java (strong OO skills preferred).
%
% Several years of large systems software design and development experience,
% with extensive knowledge of Unix/Linux.
%
% Coding skills in Python or Javascript/AJAX, database design and SQL, 
% and/or knowledge of TCP/IP and network programming are a plus.
%
% Fluency in English (reading and writing).

\beginsection {1. Profile. }\par 

\settabs
\+\indent&Working Experience:\quad&5+ years in J2EE Development (10 years total)\cr
\+&Chinese Name:                & Wu Jianfeng\cr
\+&Gender:                      & Male \cr
\+&Degree:                      & Bachelor \cr
\+&Working Experience:\quad     & $6$ years in J2EE Development\cr
\+&Mobile Phone:                & 13661788694\cr
\+&Email:                       & ueddieu@yahoo.com.cn\cr
%\+&Home Address		        & Room 502, Building 12, Nong 85, Xiangquan Road, Shanghai\cr
%\+&Postal Code		            & 200333\cr

\beginsection{2. Skills Summary. }\par
I have almost 6 years working experience in J2EE application development. 
With the solid knowledge of J2EE platform and Oracle database, I am good at performance
tuning of enterprise application. 

As a software engineer, I'd like to know how the high-level constructions are actually 
implemented in low level details. That's the reason why I spend on spend many effort on
Oracle database, Linux Kernel, Algorithm and Data Structure, Computer Architecture, 
etc., etc.  I believe it will payoff someday.

\beginsection{2.1. J2EE Platform. }\par
I have more than five years¡¯ experience of developing enterprise application in J2EE platform.
applied the following J2EE technology in my daily work since 2004: JSP, Servlet, JSTL, JDBC,
and I have 3--5 years experience in using the following frameworks, tools: Struts, Tapestry,
Spring, Hibernate, Cactus, Log4J, Axis, Tibco, JUnit, TextNG, JAXB etc., etc.
For Application Server, I usually use Tomcat in development environment and use clustered Oracle
Application Server in system testing environment. I am also familiar with WebSphere Application
am IBM certified Solution Developer---WebSphere Studio, V5.0 since October of 2004.




%I have not finish 
%reading it because of its completeness. But it inspired me to learn

%I keep self-studying algorithm and data structure even though it is not directly
%used in my daily work. From ``Introduction to Algorithm'' 
%to ``The Art of Computer Programming'', I keep reading them again and again. I 
%not only read them, but also apply the theory in practice; last week I just resolved 
%one problem---``Search Engine Arrangement Optimization'' from Google Code Jam 
%with Greedy algorithm.


\beginsection{2.2. Programming Language(Java/C++/C) and OOD }\par
I have more than 6 years' Java programming experience, I become SCJP since the 
end of 2004. 

I have good understanding of classic GOF Design Patterns, learning
Design Pattern also enforce my understanding of OO design principles.





% My coding productivity on C/C++ is quite limited, because I 
% read more than write C/C++ code and C/C++ is not used in my daily work; but 
% I know how these languages are designed and 

% Several years of large systems software design and development experience,
% with extensive knowledge of Unix/Linux.

\beginsection{2.3. Unix/Linux }\par
I always like to know how the low level details implements the high level features.
This drive me to read the Linux kernel source code, now I not only know the general 
idea of kernel, but also know how it is implemented in one specific kernel---Linux.



%I also like to read source code of famous software and see how design patterns are
%used in real software. E.g. Visitor pattern and Interpreter pattern used in Sun's 
%{\it javac} implementation impressed me a lot.
%It improves my understanding of design patterns;



%But I treat design pattern as a way to help you resvole the problem beautifully

% Coding skills in Python or Javascript/AJAX, database design and SQL, 
% and/or knowledge of TCP/IP and network programming are a plus.

\beginsection{2.4. Oracle Database. }\par
I have systematically studied the Oracle database and became OCP 
(Oracle Certified Professional) on July of 2006. 
I know the Oracle Architecture and its 
internal details, such as Execution plan, Access Path.
With those knowledge, I have succeeded in addressing performance issues in
several WEB applications. 
%The solid knowledge on Oracle database helps a lot.

\beginsection{2.1. Algorithm and Data Structure }\par
``The Art of Computer Programming'' is my favorite algorithm book, it keeps me 
interested on computer science, for example, the MMIX computer introduced in 
Fascicle 1 inspired me to learn Computer Architecture, I also implemented a 
simple MMIX simulator in Java. 



    

% Fluency in English (reading and writing).
\beginsection{2.5. English}\par
%I can apply English in daily work fluently as a second language. 
I not only can read and write technical document fluently in English, 
but also can communicate with native speaker face to face or through 
conference call.

%I also have on-site support experience 
%In order to co-develop a project on site, I have ever been to San Francisco 
%for one month on March of 2007. 
%Now we communicate with customer major through weekly conference call and email.

\beginsection{2.6 Certificates. }


\smallskip
\settabs
\+\indent&2008/09\quad&PMP (Project Management Professional)\quad&92,98,87,91\quad&\cr
\+&Date        & Certificate Name                  	& Score       & Serial Number\cr
\+&2006/07     & Oracle DBA Professional            & $92,98,87,91$ & \cr
\+&2004/10     & IBM Certified Solution Developer  	& $72$          & \cr
\+&            & ---WebSphere Studio, V5.0         	&             & \cr
\+&2004/09     & SCJP (Sun Certified Java Programmer)    & $98$          & 409182\cr
\+&2003/01     & Certified Advanced Programmer     	& $53+61$     & 02-81-13-021\cr
\+&2002/03     & Certified Programmer             	& $70+59$     & 0121400294\cr


\beginsection 3. Work Experience\par
\noindent
I started my first full-time job as Software Engineer on March 15, 2004, 
till now I have almost six years experience on J2EE platform. Before that, I have worked in 
Pharmaceutical industry for almost 5 years; 

\beginsection 3.0. Shanghai HP Inc. (Sep. 2009 -- Now)\par
I take part in the development of a pre-pay online charging product for telecommunication.
My responsibility is to develop a automation function/performance testing tool for this product.

\beginsection 3.1. Shanghai Bleum Inc. (Dec. 2004 -- Sep. 2009)\par

\noindent
I have worked in Bleum for almost 5 years. I joined Bleum as a software  
engineer, and gradually grow up to senior software engineer, technical leader,
architect, and project leader. 

\smallskip\noindent
\beginsection 3.1.1. Project Leader (May 2008 -- Sep. 2009)\par
\noindent
I start to take the full responsibility of a project, which is a public website, provide service for 
potential credit card holder---high school students or college students. 

During the past year, I lead the team deliver the projects on time and with high quality;
one of the project is customer certified zero-defect project.

We encountered performance issue in the production environment, and we successfully
addressed it from two aspects; one is to tune the SQL statement to ensure the scalability
of application, and another one is to optimize the front end performance by adopting
the best practices published by Yahoo.
  
%Since the whole team are still young, I spend many effort to train them on 
%technical skills, such as database tuning, and communication skills, such as
%how to raise question and write email to customer.

\smallskip\noindent
\beginsection 3.1.2. Architect (Oct. 2007 -- May 2008)\par
\noindent
As an architect, I start over sighting all the projects in the ODC(Offshore Development Center).
My major duty includes code review, training, evaluation, technical interview, trouble-shooting,
 technical improvement, and development process improvement. 

During this period, I have introduced GlassFish application server into one project, which 
supports hot deployment and improve the developer's productivity. (In that project, Tomcat's
hot deployment feature does not work properly because of some Axis related code.)


\beginsection 3.1.3. Technical Leader(Oct. 2006 -- October 2007)\par
\noindent
One of project during this period is to add new feature --- PDF printing for a WEB site, and to
change the looking and feel by using more pop up window. The PDF printing 
is a big challenge for us until we found a tool called PD4ML, which supports
the conversion from dynamic JSP content to PDF. We also verified that it can 
works well in the load of about twenty concurrent users. 

As the technical leader of this project. My major achievement is
the PDF printing solution based on PD4ML, which is highly appreciated by customer.

\smallskip

Another project during this period is to migrate three back end procedures
written in Toplink, those procedure are scheduled to synchronize data between 
different databases everyday. We are required to re-implement
the existing procedure and improve the performance. 

For the convenience of performance tuning, we decide to access database through JDBC.
After we finish the implementation, we measure the performance with JProfiler and identify the
bottle neck. Actually, most of time are spend in data access layer, we tune
the SQL statement and finally improved the performance to be two times better than before
(The back end procedure can finish in half an hour instead of one hour).

As the technical leader of this project. My major responsibility is
designing and performance tuning.

\beginsection 3.1.4. Senior Software Engineer (Oct. 2005 -- Oct. 2006)\par
\noindent
This project is to optimize performance of an existing application, 
since customer is not satisfied with the performance of the existing system. 
We got following lessons and experience about application performance tuning. 

First, we should consider performance requirement and perform load test in construction phase; 
Second, the load test environment should be as close to real production environment as possible,
load test environment should include same amount of data and same amount of concurrent user in database. 
Third, Hibernate may generate some unnecessary table joins, the solution
is to use native SQL instead of HQL in such case. 
Last but not the least, all the SQL Statement, including the SQL statement 
generated by Hibernate, should be reviewed to decide whether existing index 
is enough or not and what new index we need to add. 

I am the major developer of this project. I not only improved the performance
of the application (several SQL query speeds up more than ten times after tuning),
but also gain a lot of hands on experience on Oracle database.

%Another project during this period is to migrate the project from Hibernate 2
%to Hibernate 3. I pair work with my colleague and finish it in three weeks.

\beginsection 3.1.5. Software Engineer (Dec., 2004 -- Oct., 2005)\par
\noindent
The architecture of this project is a little special, the business layer is located 
in Tibco Bizwork server, and Application server  basically is a client of the 
web service published by Tibco Bizwork. The major challenge in this project 
is to resolve the issues in using Axis, for example, memory leak issue. 
We also developed a mock mechanism to develop and test WEB layer when the
 business layer is not ready. (Business layer is joint-developed simultaneously 
 by another two teams, one is in America and the other is in Singapore.)

I researched on Axis and give training about Axis to team members in the design phase. 

\beginsection 3.2. Shanghai Zhongxin Development Inc. (Mar. 2004 -- Dec. 2004)\par

\noindent
The application is deployed on Oracle 9i Application Server in the local area net. 
It is used to manage all kind of  registry and approve of Shanghai Production 
Security Administration Bureau. The Project achieved success in the use of Struts 
Framework, which saves us a lot of work. I am in charge of implementing the 
Business Flow module and System Manage module. 

My responsibility includes Designing, Coding, Unit/Integration testing of related module. 

\beginsection 3.3. Shanghai Zhongxi Pharmaceutical Inc. (May 2001 -- Mar.2004)\par

\noindent
In this period, I worked in Marketing Department providing academic support for new drugs. 
In my non-working time, I continually learning Java programming language 
and other Computer Science subject, and got the certificate of Programmer 
and Advanced Programmer. The following is two part-time projects finished during that period.

\beginsection {3.3.1. Chinese Chess Game On Internet (Sep. 2003 -- Nov. 2003). }

In this project, we need to develop a Chinese Chess Game application 
of Server/Client architecture. Its main features include negotiating 
the regulation, playing between a pairs of player through internet, 
watching other player's game, counting of time, and requesting to regret
 the step taken. The player's information is stored in the databases,
  and every game can been scored automatically by application. 

I am in charge of the design and implementation of the client side, 
implementation of chess rule in the Server side. It took me a lot of 
time to develop the GUI in client side and to integrate it with the
 server side. 

\beginsection {3.3.2. Go Game (Weiqi) Applet (May 2002 -- Aug. 2002). }

As an ancient Chinese game, Go is very complex. This program can help the
GO players to improve their skills especially skills of surviving 
in the board. With
the correct strategy stored in the data file, the applet, which is
 downloaded from Internet, can fight against the player, and beat him 
 until the player has mastered the skills. This applet improved the 
 interactivity in the teaching and learning of Go related skill. 

%I am in charge of design and implementation of the program by myself. 
%I also build a simple  temporary WEB site to test the Applet. 


\beginsection {3.4. Suzhou NO.2 Pharmaceutical Factory (July 1999 -- May 2001)}\par

\noindent
During this period, I worked in R\&D department and took part in the 
developing of a new chemical drug -- Paroxtine. My major responsibility 
includes chemical synthesis and chemical analysis. 
%At the same time, 
%I start to self-study Java programming language and other Computer Science subject. 

\beginsection {4. Education and Training}\par
\settabs\+\indent&July 2008\quad&\cr
%\+&July 2008	&PMP Training provided by Beijing Modern Project \cr
%\+&						&Management Interchange Center\cr
\+&1994-1999	&Shenyang Pharmaceutical University\cr
\+&						&Pharmacy English (5 years)\cr

% \beginsection{2.4 Source Code Reading.}\par
% I believe Source Code Reading is an important skill for software engineer.
% When I self-study Linux kernel, I read the source code when I read the book.
% The great thing is that I can understand the source code.
 

%I have studied Linux kernel in the past two years. After I read the book know how 
%it is designed, I also trace down to the source code, which make me understand the 
%Linux kernel better.%I have ever read the source code of . 

%I also spend time to read the MMIX simulator implemented by Knuth, and realize 
%how beautiful and elegant the C code could be.
%The knownledge of how kernel works helps me understand how 
%provide me a more practical and pragmatic attitude about technical.


\bye % This is the way the file ends, not with a \bang but a \bye.
