Duties and Responsibilities:
- Work on newest technologies that will improve overall SaaS application performance, such as advanced caching, distributed computing, parallel computing, and others
//memcached. parallel computing looks not suit for the SaaA applicaiotn in normal case.
- Work on platform level solutions that will address common performance issues across modules
//have to find the root case of performance issue. if it is caused by the platform level factors, we certainly should addesss it at that level.
- Work on next generation platform or technology solutions that will enable faster deliverable of customer content and increase system scalability and throughput
//throughput is important
- Work across entire engineering teams to collect performance test requirements, formulate scalable test strategies, and enforce performance testing
//performance testing or benchmarking is important to performance tuning, without it you can not know the effect of tuning, 
- Work with data center/NOC team on reproducing, resolving and preventing performance issues on production servers
//Defect prevention - same idea.
- Setup monitoring and benchmarking tools on performance lab and generate reports regularly
//daily routine task.

- Setup and execute performance and scalability tests with huge number of concurrent users, profile and fix problems.
//automation test.
- Developing test tools used to administer performance and scalability tests.
//Home grow tools.
- Profile and isolate application and architectural issues and recommend and develop resolutions.
//Challenge
- Provide internal and external customer documentation summarizing results of performance and scalability tests.
//the importance of Documentation.

Qualifications:
- BS degree in computer science or related field
- Rich software development experience -- 4 years experience with Java or J2EE.
- Have one of the following two skills:
(1) Strong experience with relational databases and SQL tuning, preferably Oracle. Or
//strong match: Oracle SQL Statement Performance Tuning.
(2). Strong experiences with HTML/CSS/Javascript or Flex and did performance tuning before
//Yahoo Front End Optimization Rule.
- Must have solid knowledge of algorithms and data structures and be able to assess trade-offs between memory vs. CPU vs. I/O vs. database load etc.
//have solid knowledge on data structure like Heap.
//CPU and I/O vs. database load trade off from Kernel design and implementation and Oracle SQL Performance tuning.
//know the trade off between performance and scalability.
- Rich experiences on resolving multi-threading, deadlocking, JVM GC issues.
//deadlock issue in Oracle Applicaiton Server when enable the session replication.
- Must be highly goal oriented, flexible and be able to adjust to changing priorities under stressful conditions and tight schedules.
//result oriented. Sucess Story: refactor one product in 2 month pair working with a team mate.
- Must have excellent communication and interpersonal skills.
//communicate with customer and different roles in the team to coordinate the project.
- An absolute self-starter. Very comfortable and highly effective when working across teams.
- Highly motivated for performance tuning work.
//I like the challenge of performanc tuning and also like the oppotunity to impact lost of people.
- Have experiences working on real, large deployment of production systems.
//our system is deployed on clustered Oracle Application Server.
- Prior experience with performance Profiling/Tuning/Testing.
//I have ever use some profiling tool, such TPTP in Earily Eclipse and Jprofiler. JMeter.
- Prior experience with analysis tools such as JProfiler, JConsole, etc.
//I have ever use some profiling tool, such Jprofiler. JMeter.

