%6/25/2009 2:09PM
%Self introduction in Architecture Call

\hsize=29pc
\vsize=42pc
\topglue 0.5in
%\magstep4
%\magnification=2500
\magnification=\magstep4
\centerline{\bf Self introduction in Architecture Call}

\beginsection 1. First 5 Years

I graduated in 1999, majored in Pharmacy, which is about the mechanism of how the
drug takes effect and how to make the drug. 

I have worked in two pharmacy factories, one for two years, another for 3 years.

On 2004, I got a job as Java Developer in a small company. The project I worked on
is to build a WEB based Office automation system for one department in Government.

On 2005, I join Bleum and at the same year, I got my baby. Now he is more than 4 years old.
he is lovely and full of energy, he bring me a lot of happiness. The only regret is that 
I did not spend enough time with him, instead 

\beginsection 2. Movement

Now I have left Bleum to persue new career oppotunities. The first try is HP, I have worked there
for about one year in the developing a real time counting system. The major assignment is to 
developing a  home grown testing system specific to the Radius/Diameter/3GPP protocol messages. 
But my interest is on the performance design in the high load; After realizing there is no opportunity
to practice in this aspect I decide to persue next job. 

\beginsection 3. Ubuntu/Gentoo Experience

I have installed the Gentoo System in my Laptop---ProBook 4416s. It takes me many time and extra fee 
for bandwidth overcharge because everything need to be downloaded and compile locally. There are 
several important impression. a) There are a few problems when compile some package. b) the compiling of 
KDE takes more than 8 hours. it verith the statement that C++ compiling is very time consuming.

Later I have installed Ubuntu 10.4.1. it looks good. for example, the chinese language support is builtin.
most of the poppular featuer such as vedio, music are out of the box. However the Live CD can not be 
boot some times, the behaviour is random, even worse, the installation on Hard Disk still have this problem.
most of the time I can not boot from it. only after some special tricky test, it works some  time. The amazing
thing is that Gentoo installation can always be booted. I am still wondering what the different is between
Gentto and Ubuntoo so that one can boot and another one can not, anyway, they are using same verison of Linux
Kernel---2.6.32.

\beginsection 4. \TeX Experiment

I always like the tools such as \TeX. I am willing to learn the design and feature since it can be covered precisely
in one short book. Maybe in the future I can use it to write my paper if I really want to persue a Master Degree in 
computer science of Operation System.


 \bye
