\hrule
\vskip 1in
\centerline{\bf a short story}
\vskip 6pt
\centerline{\sl Eddie Wu}
\vskip 0.5cm
\noindent 
I am a 
``Do you understand the math?'', my son asked.
``Sure, I know a lot about it. Are you interested on it? I can teach you
and there is a lot of fun in it.''

\lq\lq I understand.\rq\rq\ for you

a hyphen (-);
an en-dash (--);
an em-dash (---);
a minus sign ($-$).

exercise 2.1
Alice said, ``I always use an
en-dash instead of a hyphen when specifying page numbers like `480--491' in a
bibliography.''

What do you think happens when you type four hyphens in a row?
\par----
\par-----
\par------
\par-------
\par--------
\par$-$
\par$--$
\par$---$
\par$----$
\par$-----$

3/27/2009 1:56PM
\def\badcheck{A penalty has been added because your
check to us was not honored by your bank.\par}
\def\cheater{A penalty of 50\% of the underpaid tax
has been added for fraud.\par}

\badcheck
\cheater

\def\xbold{{\bf x}}%{ and } must match.
\xbold

\def\silent{I must not talk in class.\par}
\def\five{\silent \silent \silent \silent \silent \silent}
\def\twentyfive{\five \five \five \five \five}
\def\hundred{\twentyfive \twentyfive \twentyfive \twentyfive}
\hundred

\def\silent#1#2{I must not #1 in #2.}
\def\five#1#2{\silent{#1}{#2} \silent{#1}{#2} \silent{#1}{#2} \silent{#1}{#2}
 \silent{#1}{#2} \silent{#1}{#2}}
\def\twentyfive#1#2{\five{#1}{#2} \five{#1}{#2} \five{#1}{#2} \five{#1}{#2} \five{#1}{#2}}
\def\punishment#1#2{\twentyfive{#1}{#2} \twentyfive{#1}{#2}
 \twentyfive{#1}{#2} \twentyfive{#1}{#2}}
\punishment{run}{the halls}

\def\a{\b}
\def\b{A\def\a{B\def\a{C\def\a{\b}}}}
\def\puzzle{\a\a\a\a\a}
\puzzle

\def\row#1{(#1_1,\ldots,#1_n)}
$\row x$
$\row{x}$
$\row\alpha$
$\row \alpha$
$\row{x'}$
$\row{{x'}}$
$\row{\bf x}$

\def\cs #1. #2\par{first parameter is: #1 ... second parameter is: #2}
\cs You owe \$5.00. Pay it.\par

\def\cs#1. #2\par{first parameter is: #1 ... second parameter is: #2}
\cs You owe \$5.00. Pay it.\par

\def\cs #1.#2\par{first parameter is: #1 ... second parameter is: #2}
\cs You owe \$5.00. Pay it.\par

\def\cs#1.#2\par{first parameter is: #1 ... second parameter is: #2}
\cs You owe \$5.00. Pay it.\par

{\obeylines\smallskip
Roses are red,
\quad Violets are blue;
Rhymes can be typeset
\quad With boxes and glue.
\smallskip}

try something special:
% $ # % &
\$ \# \% \&
use it as special character
$a\backslash b$ 

% \ { } ^ _ ~
% $\backslash \{ \} \^ \_ \~$
$\{a^2+b_1\}$ eddie~wu
$\backslash \{ \}$

%^ _ ~
seems only allowed in math mode.
%$^$
%$_$
%$~$

%" | < >
%" | < >
{\rm Roman}

{\bf Roman}

{\it Roman}

{\sl Roman}

{\tt Roman}

\line{This text will be flush left.\hfil}
\line{\hfil This text will be flush right.}
\line{\hfil This text will be centered.\hfil}
\line{Some text flush left\hfil and some flush right.}
\line{Alpha\hfil centered between Alpha and Omega\hfil Omega}
\line{Five\hfil words\hfil equally\hfil spaced\hfil out.}

\line{\hfil\hfil What happens now?\hfil}
\line{\hfill\hfil and now?\hfil}

Mr.~\& Mrs.~User were married by
Rev.~Drofnats, who preached on Matt.~$19:3-9$.

% 84 characters
abcdefghijklmkopqrstuvwxyz
ABCDEFGHIJKLMKOPQRSTUVWXYZ
0123456789
; ! ? ( ) ` ' - * / . , @
ff ffi `` !`
fi ffl '' ?`
fl -- --- 

\vskip 1in
\hrule
\vfill\eject

\end