\hrule
\vskip 1in
\centerline{\bf a short story}
\vskip 6pt
\centerline{\sl by a. u. thor. if these is a 
very long sentense, what will happen , will it expand to several lines?
seems the line is still not long enough to show the effect. actuall it will be kept
in one line. even it will overflow the line.}
\vskip 0.5cm
once upon a time, in a distant
  gal\-axy called \"o\"o\c c,
there lived a computer
named r.~j. drofnats.

mr.~drofnats---or ``r. j.'' as
he preferred to be called---% error has been fixed.
was happiest when he was at work
typesetting beautiful documents.

{\obeylines\smallskip
Roses are red,
\quad Violets are blue;
Rhymes can be typeset
\quad With boxes and glue.
\smallskip}

try something special:
% $ # % &
\$ \# \% \&
use it as special character
$a\backslash b$ 

% \ { } ^ _ ~
% $\backslash \{ \} \^ \_ \~$
$\{a^2+b_1\}$ eddie~wu
$\backslash \{ \}$

%^ _ ~
seems only allowed in math mode.
%$^$
%$_$
%$~$

%" | < >
%" | < >
{\rm Roman}

{\bf Roman}

{\it Roman}

{\sl Roman}

{\tt Roman}

\line{This text will be flush left.\hfil}
\line{\hfil This text will be flush right.}
\line{\hfil This text will be centered.\hfil}
\line{Some text flush left\hfil and some flush right.}
\line{Alpha\hfil centered between Alpha and Omega\hfil Omega}
\line{Five\hfil words\hfil equally\hfil spaced\hfil out.}

\line{\hfil\hfil What happens now?\hfil}
\line{\hfill\hfil and now?\hfil}

Mr.~\& Mrs.~User were married by
Rev.~Drofnats, who preached on Matt.~$19:3-9$.

% 84 characters
abcdefghijklmkopqrstuvwxyz
ABCDEFGHIJKLMKOPQRSTUVWXYZ
0123456789
; ! ? ( ) ` ' - * / . , @
ff ffi `` !`
fi ffl '' ?`
fl -- --- 

\vskip 1in
\hrule
\vfill\eject

